Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2023-05-28 src/sections/fidanka.tex
Transed-Name

While there are many packages which can measure fiducial lines very well
{\color{red}[CITATIONS]}, we do not belive that any of these perfectly match
our use case. Therefore, we elect to develope our own software suite,
\fidanka. \fidanka is a python package designed to automate
much of the process of measuring fiducual lines in CMDs, adhearing to the four
criteria we lay out above. Primary features of \fidanka may be seperated into
two categories: stellar population synthethis and isochrone
optimization/fitting (distance modulus, B-V color excess, and binpary mass
fraction)

@@

\fidanka uses MIST formated isochrones {\color{red}[CITATION]} as input along
with distance modulus, B-V color excess, binary mass fraction, and bolometric
corrections. An arbitrarily large number of isochrones may be used to define an
arbitrary number of populations. Synthetic stars are samples from each
isochroner based on a definiable probability (for example it is belived that
$\sim90\%$ of stars in globular clusters are younger population
{\color{red}[CITATION]). Based on the metallicity, $\mu$, and E(B-V) of each
isochrone, bolometric corrections are taken from bolometric correction
tables. Where bolometric correction tables do not include exact metallicities
or extinctions a linear interpolation is preformed between the two bounding
values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
from a set of 2 NGC 2808 isochrones as well as a comparison between those isochrones and
the measured fiducual line of the synthetic population.

>>>>

While there are many packages which can measure fiducial lines very well
{\color{red}[CITATIONS]}, we do not belive that any of these perfectly match
our use case. Therefore, we elect to develope our own software suite, \fidanka.
\fidanka is a python package designed to automate much of the process of
measuring fiducual lines in CMDs, adhearing to the four criteria we lay out
above. Primary features of \fidanka may be seperated into three primary
categories: fiducual line measurment, stellar population synthethis, and
isochrone optimization/fitting. Additionally, there are utility functions which
are detailed in the \fidanka documentation.

@@

\fidanka uses MIST formated isochrones {\color{red}[CITATION]} as input along
with distance modulus, B-V color excess, binary mass fraction, and bolometric
corrections. An arbitrarily large number of isochrones may be used to define an
arbitrary number of populations. Synthetic stars are samples from each
isochroner based on a definiable probability (for example it is belived that
$\sim90\%$ of stars in globular clusters are younger population
{\color{red}[CITATION]}). Based on the metallicity, $\mu$, and E(B-V) of each
isochrone, bolometric corrections are taken from bolometric correction tables.
Where bolometric correction tables do not include exact metallicities or
extinctions a linear interpolation is preformed between the two bounding
values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
from a set of 2 NGC 2808 isochrones as well as a comparison between those
isochrones and the measured fiducual line of the synthetic population.

\subsection{Isochrone Optimization}
The optimization routines in \fidanka will find the best fit distance modulus,
B-V color excess, and binary number fraction for a given set of isochrones. If
a single isochrone is provided then the optimization is done by mimizing the
$\chi^2$ of the perpendicular distnaces between an isochrone and a fiducual
line. If multiple isochrones are provided then those isochrones are first used
to run stellar population synthethis and generate a synthetic CMD. The
optimization is then done by mimizing the $\chi^2$ of both the perpendicular
distnaces between and widths of the observed fiducual line and the fiducual
line of the synthetic CMD.
